Measuring contrast processing in the visual system using SSVEP

### 2024-04-07 review.qmd
Fix bugs

# Amblyopia parameters would follow a similar structure if they were provided.
# Since they're not detailed in your R code, I'll move on to the autism plot.

@@

plt.subplot(2, 2, 4)  # Fourth plot for Parkinson's
plt.plot(finecontrastsdB, respParkPatients, lw=4, color='red', label='Parkinson\'s patients')
plt.plot(finecontrastsdB, respParkControls, lw=4, color='black', linestyle='--', label='Control participants')
plt.xticks(ticklocsx, ticklabelsx)
plt.yticks(np.arange(0, 7, 2))
plt.xlabel('Target contrast (%)')
plt.ylabel('SSVEP response')
plt.title("(d) Parkinson's")
plt.legend()
# To save the figure
plt.savefig('clinicalplot.pdf')
```

<!---
```{r}

pdf('Figures/clinicalplot.pdf',width=12,height=10)
par(mfrow=c(2,2))

finecontrastsdB <- seq(-18,36,1)
finecontrasts <- 10^(finecontrastsdB/20)
ticklocsx <- seq(-18,36,6)
ticklabelsx <- c('1/8','1/4','1/2',1,2,4,8,16,32,64)

# fits to data from Tsai et al. (2011)
epilepsyparams <- matrix(0,nrow=2,ncol=4)
epilepsyparams[1,] <- c(3.4,0.15,1.4,1)  # controls
epilepsyparams[2,] <- c(5.3,0.23,1.4,1)  # patients

respEPIcontrols <- epilepsyparams[1,1] * ((finecontrasts/100)^epilepsyparams[1,3]/(epilepsyparams[1,2]^epilepsyparams[1,3] + (finecontrasts/100)^epilepsyparams[1,3])) + epilepsyparams[1,4]

respEPIpatients <- epilepsyparams[2,1] * ((finecontrasts/100)^epilepsyparams[2,3]/(epilepsyparams[2,2]^epilepsyparams[2,3] + (finecontrasts/100)^epilepsyparams[2,3])) + epilepsyparams[2,4]

ticklocsy <- seq(0,6,2)
ticklabelsy <- ticklocsy

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-18,36), ylim=c(0,6))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="SSVEP response", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main='(a) Epilepsy',cex.main=2)

lines(finecontrastsdB,respEPIpatients,lwd=4,col='blue')
lines(finecontrastsdB,respEPIcontrols,lwd=4,lty=2,col='black')

legend(-18,6,c('Epilepsy patients','Control participants'),lwd=4,lty=c(1,2),col=c('blue','black'),box.lwd=2)

ticklocsy <- seq(0,6,2)
ticklabelsy <- ticklocsy

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-18,36), ylim=c(0,6))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="SSVEP response", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

title(main='(b) Amblyopia',cex.main=2)

# fits to data from Vilidaite et al (2018)
autismparams <- matrix(0,nrow=2,ncol=4)
autismparams[1,] <- c(0.6253,0.2701,125550,5.6199)  # ASD group
autismparams[2,] <- c(1.0131,0.3369,3589900,6.8622) # control group

respASD <- (autismparams[1,1]*(finecontrasts^autismparams[1,4])/(autismparams[1,3] + finecontrasts^autismparams[1,4])) + autismparams[1,2]
respCON <- (autismparams[2,1]*(finecontrasts^autismparams[2,4])/(autismparams[2,3] + finecontrasts^autismparams[2,4])) + autismparams[2,2]

ticklocsy <- seq(0,1.5,0.5)
ticklabelsy <- ticklocsy

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-18,36), ylim=c(0,1.5))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="SSVEP response", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main='(c) Autism',cex.main=2)

lines(finecontrastsdB,respASD,lwd=4,col='darkgreen')
lines(finecontrastsdB,respCON,lwd=4,lty=2,col='black')

legend(-18,1.5,c('ASD children','Control children'),lwd=4,lty=c(1,2),col=c('darkgreen','black'),box.lwd=2)

ticklocsy <- seq(0,6,2)
ticklabelsy <- ticklocsy

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-18,36), ylim=c(0,6))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="SSVEP response", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main="(d) Parkinson's",cex.main=2)

dev.off()

``` commented out R because of the weird reticulate bug...--->

![caption.](Figures/clinicalplot.pdf){#fig-plotclinical}

>>>>

amblyparams = np.array([
    [0.39, 37.2, 1.4, 0.22],  # amblyopic eye
    [2.33, 111.69, 1.4, 0.22]   # fellow eye
])

# Calculate responses
respambly = amblyparams[0,0] * ((finecontrasts)**amblyparams[0,2] /
                (amblyparams[0,1] + (finecontrasts)**amblyparams[0,2])) + amblyparams[0,3]

respfellow = amblyparams[1,0] * ((finecontrasts)**amblyparams[1,2] /
                (amblyparams[1,1] + (finecontrasts)**amblyparams[1,2])) + amblyparams[1,3]

plt.subplot(2, 2, 2)
plt.plot(finecontrastsdB, respambly, lw=4, color='red', label='Amblyopic eye')
plt.plot(finecontrastsdB, respfellow, lw=4, color='black', linestyle='--', label='Fellow eye')
plt.xticks(ticklocsx, ticklabelsx)
plt.yticks(np.arange(0, 2.5, 0.5))
plt.xlabel('Target contrast (%)')
plt.ylabel('SSVEP response')
plt.title('(b) Amblyopia')
plt.legend()

@@

plt.subplot(2, 2, 4)  # Fourth plot for Parkinson's
plt.plot(finecontrastsdB, respParkPatients, lw=4, color='red', label='Parkinson\'s patients')
plt.plot(finecontrastsdB, respParkControls, lw=4, color='black', linestyle='--', label='Control participants')
plt.xticks(ticklocsx, ticklabelsx)
plt.yticks(np.arange(0, 7, 2))
plt.xlabel('Target contrast (%)')
plt.ylabel('SSVEP response')
plt.title("(d) Parkinson's")
plt.legend()
# To save the figure
plt.savefig('Figures/clinicalplot.pdf')

![Example contrast response functions for different clinical conditions. Panel (a) shows modelled contrast response functions for epilepsy patients (blue) and control participants (black), based on the data of Tsai et al. (2011). Panel (b) shows functions for the amblyopic (red) and fellow (black) eyes of adults with amblyopia, based on the data of Baker et al. (2015). Panel (c) shows functions for children with (green) and without (black) a diagnosis of autism, based on the data of Vilidaite et al. (2018). Panel (d)...](Figures/clinicalplot.pdf){#fig-plotclinical}
